Secondary analysis of tables

### 2019-09-21 Analysis/Analysis_Tables_New.Rmd
Fix plots to use latest estimates

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Autoimmune", mtx_traits = mtx0, databases = "Biogrid"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Cancer", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular disease", mtx_traits = mtx0, databases = "Biogrid"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye disease", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic disease", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_neurologic <- plot(mtx_traits_selected_dotplot(category = "Neurologic", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_psychiatric <- plot(mtx_traits_selected_dotplot(category = "Psychiatric", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))

png(filename = "../manuscript/Figures/FigS4_summary_diseases_Biogrid.png", height = 8, width = 14, units = "in", res = 300)
lay1 <- rbind(c(1, 2, 3, 4))
lay2 <- rbind(c(1, 2, 3, 4))
g1 <- arrangeGrob(grobs = list(p_intelligence, p_anthropometric, p_neurologic, p_psychiatric), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_cardiovascular, p_metabolic, p_eye), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

>>>>

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Autoimmune", mtx_traits = mtx0, databases = "Biogrid"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Cancer", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular disease", mtx_traits = mtx0, databases = "Biogrid"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye disease", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic disease", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
# p_neurologic <- plot(mtx_traits_selected_dotplot(category = "Neurologic", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_psychiatric <- plot(mtx_traits_selected_dotplot(category = "Psychiatric", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))

png(filename = "../manuscript/Figures/FigS4_summary_diseases_Biogrid.png", height = 8, width = 12, units = "in", res = 300)
lay1 <- rbind(c(1, 2, 3))
lay2 <- rbind(c(1, 2, 3))
g1 <- arrangeGrob(grobs = list(p_intelligence, p_anthropometric, p_psychiatric), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_cardiovascular, p_metabolic, p_eye), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```
